Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-21 snapshot_system/failover.tex
Added several figures (VM Availability, CDS Replication, container links

The rate of increase in node failures can be seen in Figure~\ref{fig-vm-failure}
(for a 100 node cluster).
The graph assumes 10X40GB snapshots per VM with 18\% unique data after local
dedup and 64MB filesytem chunks (which results in 1792 filesystem chunks per
VM). We assume 18\% unique data after local dedup because that is what our
snapshots have shown.

@@

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Failed storage nodes},
		ylabel={Chance VM is affected (\%)},
		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
                mark options=solid,
                legend pos=north west
		]
                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO]{figures/vm_failure_1.txt};
                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_1.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_1.txt};
                \addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_1.txt};
                \legend{$VO$,$VC_{C_R=3}$,$VC_{C_R=4}$,$VC_{C_R=5}$,$VC_{C_R=6}$,$VC_{C_R=7}$}
		\end{axis}
	\end{tikzpicture}
  \caption{Percent chance that a VM is affected as storage nodes fail}
  \label{fig-vm-failure}
\end{figure}

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Failed storage nodes},
		ylabel={Chance VM is affected (\%)},
		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
                mark options=solid,
                legend pos=north west
		]
                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO1]{figures/vm_failure_2.txt};
                \addplot[densely dashed,color=blue,mark=square*] table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
                \addplot[densely dashed,color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
                \addplot[densely dashed,color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
                \legend{$VO_{C=5}$,$VO_{C=10}$,$VO_{C=20}$,$VO_{C=40}$,$VC_{C=100}$,$VC_{C=200}$,$VC_{C=400}$,$VC_{C=800}$}
		\end{axis}
	\end{tikzpicture}
  \caption{Percent chance that a VM is affected as storage nodes fail}
  \label{fig-vm-failure}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Block links},
		xlabel={Number of VMs added},
		ylabel={Avg. Links to a Block},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		legend pos=south east
		]
		\addplot[color=blue,mark=*] table[x=VMs,y=Measured] {figures/vo_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=Theoretical] {figures/vo_links.txt};
		\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Average number of VMs sharing a block in the global index}
  \label{fig-vo-links}
\end{figure}
\comments{
	=  sum _for_all_block(   Probablity (a block fails) *number of VM sharing this block ))
               = Probability(a block fails) * sum_for_all_blocks (numb of VM shared)
	= Probablity (a block fails) *b *aveageLengthVM
	= [ 1-  C(r, k) /C(n,r)] * b* [ 1+ s *V(1-1/ln V)]

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%OLD MODEL START%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%The rate of increase in node failures can be seen in Figure~\ref{fig-vm-failure}
%(for a 100 node cluster).
%The graph assumes 10X40GB snapshots per VM with 18\% unique data after local
%dedup and 64MB filesytem chunks (which results in 1792 filesystem chunks per
%VM). We assume 18\% unique data after local dedup because that is what our
%snapshots have shown.

@@

\comments{\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Failed storage nodes},
		ylabel={Chance VM is affected (\%)},
		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
                mark options=solid,
                legend pos=north west
		]
                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO]{figures/vm_failure_1.txt};
                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_1.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_1.txt};
                \addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_1.txt};
                \legend{$VO$,$VC_{C_R=3}$,$VC_{C_R=4}$,$VC_{C_R=5}$,$VC_{C_R=6}$,$VC_{C_R=7}$}
		\end{axis}
	\end{tikzpicture}
  \caption{Percent chance that a VM is affected as storage nodes fail}
  \label{fig-vm-failure}
\end{figure}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%OLD MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL START%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Failed storage nodes},
		ylabel={VM Availability (\%)},
		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                }
		]
                \addplot[densely dashed,color=blue,mark=square*] table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO1]{figures/vm_failure_2.txt};
                %\addplot[densely dashed,color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
                %\addplot[densely dashed,color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_2.txt};
                %\addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
                %\addplot[color=red,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
            \legend{$VO\,10$,$VO\,5$,$VC\,1000$,$VC\,11$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail for VO and VC models for varying average block link counts (i.e. average number of VMs that use a block)}
  \label{fig-vm-availability}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={CDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Availability (\%)},
		%extra y ticks={4.5,5.5,6.5} %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                }
		]
                \addplot[color=blue,mark=*] table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
                \addplot[color=blue,mark=square*] table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
                \addplot[color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
                \addplot[color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
            \legend{$R_C=3$,$R_C=4$,$R_C=5$,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different CDS Replication factors (Non-CDS replication fixed at 3, and average CDS block links set to 1000)}
  \label{fig-cds-replication}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Block links},
		xlabel={Number of VMs added},
		ylabel={Avg. Links to a Block},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		legend pos=south east
		]
		\addplot[color=blue,mark=*] table[x=VMs,y=Measured] {figures/vo_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=Theoretical] {figures/vo_links.txt};
		\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Average number of VMs sharing a block in the global index}
  \label{fig-vo-links}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Container links},
		xlabel={Number of VMs},
		ylabel={Avgerage Container links},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		]
		\addplot[color=blue,mark=*] table[x=VMs,y=ContainerLinks] {figures/vo_container_links.txt};
		%\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a container in the global index (for VO)}
  \label{fig-vo-container-links}
\end{figure}

\comments{
	=  sum _for_all_block(   Probablity (a block fails) *number of VM sharing this block ))
               = Probability(a block fails) * sum_for_all_blocks (numb of VM shared)
	= Probablity (a block fails) *b *aveageLengthVM
	= [ 1-  C(r, k) /C(n,r)] * b* [ 1+ s *V(1-1/ln V)]
